Time and space specifications for stencils

### 2016-03-17 paper.tex
product of stencils syntax

\begin{figure}
\begin{align*}
\textit{specs} ::= & \; \textit{spec} \; \texttt{;} \; \textit{specs} \, \mid \, \textit{spec} \\
%
\textit{spec} :: = & \; \texttt{v} : S \\[0.5em]
S ::= &  \; \texttt{forward} \; [\texttt{depth=}\textit{depth}] \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{backward} \; [\texttt{depth=}\textit{depth}] \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{centered} \; [\texttt{depth=}\textit{depth}] \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{unspecified} \; [\texttt{dims=}\textit{dims}] \\
& \; \mid \texttt{read-once} \; S \\[0.5em]
\textit{depth} ::= & \; \mathbb{N} \, \mid \, \textit{temp-spec} \\ 
\textit{temp-spec} ::= & \; \mathbb{N}\{var\} \\
\textit{dims} ::= & \; \mathbb{D} \; \texttt{,} \; \textit{dims} \, \mid
                    \, \mathbb{D} \\
\mathbb{D}  ::= & \; \mathbb{N}_{>0} \, \mid \, \texttt{t}
\end{align*}
\caption{Syntax of specifications}
\label{fig:syntax}
\end{figure}

>>>>

\begin{figure}
\begin{align*}
\textit{specs} ::= & \; \textit{spec} \; \texttt{;} \; \textit{specs} \, \mid \, \textit{spec} \\
%
\textit{spec} :: = & \; \texttt{v} : S \\[0.5em]
S ::= &  \; \texttt{forward}, \; [\texttt{depth=}\textit{depth}], \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{backward}, \; [\texttt{depth=}\textit{depth}], \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{centered}, \; [\texttt{depth=}\textit{depth}], \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{unspecified}, \; [\texttt{dims=}\textit{dims}] \\
& \; \mid \textit{spec} \; \texttt{\&} \; \textit{spec} \\
& \; \mid \texttt{read-once} \; S \\[0.5em]
\textit{depth} ::= & \; \mathbb{N} \, \mid \, \textit{temp-spec} \\ 
\textit{temp-spec} ::= & \; \mathbb{N}\{var\} \\
\textit{dims} ::= & \; \mathbb{D} \; \texttt{,} \; \textit{dims} \, \mid
                    \, \mathbb{D} \\
\mathbb{D}  ::= & \; \mathbb{N}_{>0} \, \mid \, \texttt{t}
\end{align*}
\caption{Specification syntax}
\label{fig:syntax}
\end{figure}
